---
title: "CodingChallenge7"
author: "Priya Shahi"
date: "2026-04-01"
output: 
  word_document:
     toc: true 
  md_document:
    variant: gfm
  html_document:
    df_print: paged
  pdf_document: default
---
# Question 1
```{r CodingChallenege7}
library(tidyverse)
library(lme4)
library(emmeans)
library(multcomp)
library(multcompView)
```

```{r}
Plant <- read.csv("PlantEmergence.csv")
Plant$Treatment <- as.factor(Plant$Treatment)
Plant$DaysAfterPlanting <- as.factor(Plant$DaysAfterPlanting)
Plant$Rep <- as.factor(Plant$Rep)
```

# Question 2
```{r}
model <- lm(Emergence~Treatment*DaysAfterPlanting, data = Plant)
summary(model)
anova(model)
```

# Question 3
- No, we do not need to fit the interaction term.
```{r}
model_simple <- lm(Emergence ~ Treatment + DaysAfterPlanting, data = Plant)
summary(model_simple)
anova(model_simple)
```
Intercept (182.163),Treatment 2 Coefficient (−134.531)

# Question 4
```{r}
lsmeans <- emmeans(model_simple, ~Treatment) #leastSquared means
Results_lsmeans <- cld(lsmeans, alpha = 0.05, reversed = TRUE, details = TRUE)

```
Interpret:The least square means (LSMeans) and Tukey grouping show that Treatment 2 is significantly different from all other treatments.

# Question 5
```{r}
plot_cldbars_onefactor <- function(lm_model, factor) {
data <- lm_model$model
variables <- colnames(lm_model$model)
dependent_var <- variables[1]
independent_var <- variables[2:length(variables)]
lsmeans <- emmeans(lm_model, as.formula(paste("~", factor))) # estimate
lsmeans
Results_lsmeans <- cld(lsmeans, alpha = 0.05, reversed = TRUE, details =
TRUE, Letters = letters) # contrast with Tukey adjustment by default.
# Extracting the letters for the bars
sig.diff.letters <- data.frame(Results_lsmeans$emmeans[,1],
str_trim(Results_lsmeans$emmeans[,7]))
colnames(sig.diff.letters) <- c(factor, "Letters")
# for plotting with letters from significance test
ave_stand2 <- lm_model$model %>%
group_by(!!sym(factor)) %>%
dplyr::summarize(
ave.emerge = mean(.data[[dependent_var]], na.rm = TRUE),
se = sd(.data[[dependent_var]]) / sqrt(n())
) %>%
left_join(sig.diff.letters, by = factor) %>%
mutate(letter_position = ave.emerge + 10 * se)
plot <- ggplot(data, aes(x = !! sym(factor), y = !! sym(dependent_var))) +
stat_summary(fun = mean, geom = "bar") +
stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
ylab("Number of emerged plants") +
geom_jitter(width = 0.02, alpha = 0.5) +
geom_text(data = ave_stand2, aes(label = Letters, y = letter_position),
size = 5) +
xlab(as.character(factor)) +
theme_classic()
return(plot)
}
plot_cldbars_onefactor(model_simple, "Treatment")
```

The intercept represents the mean emergence for the reference treatment at the reference day level, and the coefficient for Treatment 2 shows how much emergence differs from the reference treatment after adjusting for DaysAfterPlanting.

# Question 6
[Github](https://github.com/ShahiPriya1/Reproducibility-Class/blob/main/CodingChallenge/Md_File/Codingchallenge7.md) 


